---
title: "api_NASA"
author: "Aggie"
date: "12/21/2020"
output: html_document
---

NASA API thingy data

location of space station and how many people are currently in space

first: how many people in space

```{r}
library(httr)
people_api_data <- GET("http://api.open-notify.org/astros.json") # output is a list with info retruned by api server
people_api_data
people_content <- content(people_api_data)
people_content # returns list of 3
```

In its current state, the data in the people_api_data variable is not usable. The actual data is contained as raw Unicode in the people_api_data list, which ultimately needs to be converted into JSON format.

```{r}
# rawToChar(people_api_data$content) # converting first to character vector
people_data <- jsonlite::fromJSON(rawToChar(people_api_data$content))
people_data$people
```

Answer: there is currently 7 people in space



### what if we want to know when the intl space station will pass over a certain location? OR its current location?

```{r}
location_ISS  <- GET("http://api.open-notify.org/iss-now.json")
location <- content(location_ISS)
location$iss_position
location$timestamp # time is in unix time
```

finding out when the ISS will be passing over the Brooklyn Bridge (which is at roughly latitude 40.7, longitude: -74)


Open Notify’s ISS Pass Times API requires us to provide additional parameters before it can return the data we want.

Specifically, we'll need to specify the latitude and longitude of the location we're asking about as part of our GET() request. Once a latitude and longitude are specified, they are combined with the original URL as query parameters.

```{r}
specific_location <- GET("http://api.open-notify.org/iss-pass.json",
                         query = list(lat = 40.7, lon = -74))

spec_location <- jsonlite::fromJSON(rawToChar(specific_location$content))
spec_location$response
```